%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
\begin{center}
    {\Huge \scshape Prince Yadav} \\ \vspace{1pt}
    Gorakhpur, Uttar Pradesh 273402 \\ \vspace{1pt}
    \small \raisebox{-0.1\height}\faPhone\ +91 7080523171 ~ \href{mailto:prince041670@gmail.com}{\raisebox{-0.2\height}\faEnvelope\  \underline{prince041670@gmail.com}} ~ 
    \href{https://linkedin.com/in/prince-yadav-331bb5298/}{\raisebox{-0.2\height}\faLinkedin\ \underline{linkedin.com/in/prince-yadav-331bb5298/}}  ~
    \href{https://github.com/PrinceYadav001}{\raisebox{-0.2\height}\faGithub\ \underline{github.com/PrinceYadav001}}
    \vspace{-8pt}
\end{center}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Galgotias University}{Sep. 2023 -- May 2027}
      {Bachelor of Science in Computer Science}{Greater Noida, Uttar Pradesh}
  \resumeSubHeadingListEnd

%------RELEVANT COURSEWORK-------
\section{Relevant Coursework}
        \begin{multicols}{4}
            \begin{itemize}[itemsep=-5pt, parsep=3pt]
                \item\small Data Structures
                \item Software Methodology
                \item Algorithms Analysis
                \item Database Management
                \item Machine Learning
            \end{itemize}
        \end{multicols}
        \vspace*{2.0\multicolsep}

%-----------CERTIFICATIONS-----------
\section{Certifications}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Data Structures \& Algorithms in Java}{: Apna College, 2024} \\
     \textit{Arrays, Linked Lists, Trees, Graphs, Algorithm Optimization, Problem-solving with Java} \\
     \textbf{Full Stack MERN Development}{: Apna College, 2024} \\
     \textit{MongoDB, Express.js, React.js, Node.js, REST APIs, Authentication, Deployment}
    }}
 \end{itemize}
 \vspace{-16pt}

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Smart India Hackathon (SIH) 2025}{September 2025}
      {Full-Stack Developer - Top 50 Internal Finalist}{Galgotias University}
      \resumeItemListStart
        \resumeItem{Selected as finalist from Galgotias University to represent the institution in Grand SIH 2025 competition.}
        \resumeItem{Developed IoT-based project for monitoring river conditions and predicting floods using real-time data analysis.}
        \resumeItem{Demonstrated innovation in environmental technology and problem-solving for disaster management solutions.}
      \resumeItemListEnd

    \resumeSubheading
      {Personal Development Projects}{January 2024 -- Present}
      {Full-Stack Developer}{Self-Directed}
      \resumeItemListStart
        \resumeItem{Developed Wanderlust, an Airbnb-like rental platform with secure authentication and property CRUD operations.}
        \resumeItem{Implemented RESTful APIs using Node.js, Express.js, and MongoDB following MVC architecture.}
        \resumeItem{Built responsive frontend with EJS templating and integrated error-handling middleware for robust routing.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd
\vspace{-16pt}

%-----------PROJECTS-----------
\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Wanderlust - Property Rental Platform} $|$ \emph{Node.js, Express.js, MongoDB, EJS, Bootstrap}}{November 2024}
          \resumeItemListStart
            \resumeItem{Developed a full-stack web application similar to Airbnb for property rentals with user authentication and listing management.}
            \resumeItem{Implemented secure user authentication using Passport.js and integrated Cloudinary API for image uploads.}
            \resumeItem{Built RESTful APIs with Express.js for CRUD operations and integrated Mapbox API for interactive maps.}
            \resumeItem{Designed responsive frontend using EJS templating engine and Bootstrap framework with MongoDB database.}
          \resumeItemListEnd
          \vspace{-13pt}
      \resumeProjectHeading
          {\textbf{IoT River Monitoring System} $|$ \emph{IoT, Data Analysis, Real-time Monitoring}}{September 2024}
          \resumeItemListStart
            \resumeItem{Developed IoT-based project for monitoring river conditions and predicting floods using real-time data analysis.}
            \resumeItem{Implemented sensor integration and data processing algorithms for environmental disaster management.}
            \resumeItem{Selected as SIH 2025 finalist project representing Galgotias University in national competition.}
          \resumeItemListEnd
          \vspace{-13pt}
      \resumeProjectHeading
          {\textbf{Digital Knowledge Sharing Platform} $|$ \emph{Web Development, Clean Technology}}{August 2024}
          \resumeItemListStart
            \resumeItem{Built scalable web platform promoting Water-Efficient Techniques for sustainable farming practices.}
            \resumeItem{Implemented user-friendly interface for sharing agricultural knowledge and green technology solutions.}
            \resumeItem{Qualified for SIH 2024 pre-selection round, recognized for innovative problem-solving in Software category.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd
\vspace{-15pt}

%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: JavaScript, HTML/CSS, SQL, Python, Java} \\
     \textbf{Frontend Development}{: React.js, EJS, Bootstrap, CSS3, HTML5, Responsive Design} \\
     \textbf{Backend Development}{: Node.js, Express.js, RESTful APIs, Middleware, Authentication (Passport.js)} \\
     \textbf{Databases}{: MongoDB, Mongoose, MySQL} \\
     \textbf{Developer Tools}{: VS Code, Git, GitHub, npm, Postman, Eclipse} \\
     \textbf{Cloud \& Services}{: Cloudinary, Mapbox API, Deployment (Render/Vercel)} \\
     \textbf{Other Technologies}{: IoT, Data Analysis, MVC Architecture, Session Management}
    }}
 \end{itemize}
 \vspace{-16pt}

\end{document}